\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-12 Dissertation/Defense/defense.tex
done except for putting in updated videos (3)
completed with videos, need tlee edits applied still

\begin{minipage}[t]{5.0cm}
\vspace*{0.5cm}
\begin{itemize}
	\item A standard \emph{approximate} inverse sensor model technique is compared with the proposed \emph{exact} method
\end{itemize}
\end{minipage}
\begin{minipage}[t]{5.0cm}
%\vspace*{0.5cm}
\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_inf_19.pdf}
        \caption*{Approximate}
    \end{subfigure}
    \hspace*{-0.1\textwidth}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_inf_19.pdf}
        \caption*{Exact}
    \end{subfigure}
\end{figure}
\end{minipage}

\begin{itemize}
\item The exact algorithm yields a more \emph{certain} map from the same measurement set
\end{itemize}

@@

% TODO: uncomment!
%\begin{frame}
%	\frametitle{Numerical Results}
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=IRL.mp4,
%  		flashvars={source=IRL.mp4}
%		]{}{VPlayer.swf}
%		}
%\end{frame}

%\frametitle{Experimental Results}
%	\centering{
%	\includemovie[poster,autoplay]{0.720\textwidth}{0.576\textwidth}{JIRS16_experiment_SideBySide_speedup8x.mov}}
%\end{frame}

@@

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Exploration}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
%  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Patrol}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
%  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: uncomment!
%\begin{frame}
%\frametitle{Ground Experiment Video}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=NRL_ground_test.mp4,
%  		flashvars={source=NRL_ground_test.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: uncomment!
%\begin{frame}
%\frametitle{Large Flight Test Experiment Video}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=nrl_experiment_narrated.mp4,
%  		flashvars={source=nrl_experiment_narrated.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: uncomment! and update!
%\begin{frame}
%\frametitle{Full 3D Flying Experiment Video}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=gwu_experiment_narrated.mp4,
%  		flashvars={source=gwu_experiment_narrated.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: update with dissertation version!

>>>>

\begin{itemize}
	\item A standard \emph{approximate} inverse sensor model technique is compared with the proposed \emph{exact} method
	\item The exact algorithm yields a more \emph{certain} map from the same measurement set
\end{itemize}

%\vspace*{0.5cm}
\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_19.pdf}
        \caption*{Approx. Map}
    \end{subfigure}
%    \hspace*{-0.1\textwidth}
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_19.pdf}
        \caption*{Exact Map}
    \end{subfigure}
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_inf_19.pdf}
        \caption*{Approx. $H$}
    \end{subfigure}
%    \hspace*{-0.1\textwidth}
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_inf_19.pdf}
        \caption*{Exact $H$}
    \end{subfigure}
\end{figure}

@@

\begin{frame}
	\frametitle{2D Autonomous Exploration: Intel Research Lab}
	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=IRL.mp4,
  		flashvars={source=IRL.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

\begin{frame}
	\frametitle{3D Autonomous Exploration: Mars}
	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=Topological Mars Mapping and Autonomous Exploration in 3D.mp4,
  		flashvars={source=Topological Mars Mapping and Autonomous Exploration in 3D.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

@@

\begin{frame}
\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Exploration}

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
		]{}{VPlayer.swf}
		}

@@

\begin{frame}
\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Patrol}

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
		]{}{VPlayer.swf}
		}

\begin{frame}
\frametitle{Cell Degradation and Patrol}

\begin{figure}
	\centering
	\includegraphics[width=0.65\textwidth]{entropy_patrol_9minSwitch.pdf}
\end{figure}

\begin{itemize}
	\item Entropy of the map increases if patrol stops at $9$ minutes if cell degradation continues
\end{itemize}

@@

\begin{frame}
\frametitle{Ground Experiment Video}

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=NRL_ground_test.mp4,
  		flashvars={source=NRL_ground_test.mp4}
		]{}{VPlayer.swf}
		}

@@

\begin{frame}
\frametitle{Large Flight Test Experiment Video}

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=NRL_3D_large_space.mp4,
  		flashvars={source=NRL_3D_large_space.mp4}
		]{}{VPlayer.swf}
		}

@@

\begin{frame}
\frametitle{Full 3D Flying Experiment Video}

	\centering{
		\includemedia[
  		width=0.720\textwidth,
  		height=0.576\textwidth,
  		activate=pageopen,
  		addresource=explore3D_SEH.mp4,
  		flashvars={source=explore3D_SEH.mp4}
		]{}{VPlayer.swf}
		}

@@
